\begin{frame}
\frametitle{Introduction}
\begin{block}{What is subspace correction method?}
A framework for various iterative methods.
\end{block}
Jacobi and
Gauss-Seidel iterations, domain decomposition methods,
multigrid methods and so on, 
can be viewed as two basic types:
\begin{itemize}
\item parallel subspace correction(PSC)
\item successive subspace correction(SSC)
\end{itemize}
with different 
space decompositions and subspace corrections.

\begin{block}{Why bother to do it?}
A feature of this framework is that a quite general 
abstract convergence theory can be established.
\end{block}
\end{frame}

\begin{frame}
\begin{block}{Subspace Decomposition}
A decomposition of $V$ consists of a number of subspaces
$V_i \subset V$ such that
$$V=\sum_{i=1}^JV_i$$
\end{block}

For each $i$, we define $\Pi_i'$ and $\Pi_i^*: V \mapsto V_i$ by 
$$(\Pi_i'v,v_i):=(v,v_i)\quad (\Pi_i^*v,v_i)_A:=(v,v_i)_A
\quad v\in V,v_i\in V_i$$
and $A_i:V_i \mapsto V_i$ by
$$(A_iu_i,v_i):=(Au_i,v_i)\quad u_i,v_i \in V_i$$
By definition, we get
$$A_i\Pi_i^*=\Pi_i'A$$

For $Au=f$, so we get
\begin{block}{Subspace equation}
$$A_i u_i =f_i,
\text{ where } u_i=\Pi_i^* u
\text{ and }f_i=\Pi_i'f$$
\end{block}
\end{frame}

\begin{frame}
The subspace equation will be in general solved approximately.

To describe this, we define $$R_i: V_i \mapsto V_i$$
which approximates 
$A_i^{-1}$ in certain sense.

\begin{block}{Example}
$$\mathbb{R}^n=\sum_{i=1}^{n}\mathrm{span}\{e_i\}$$
where $e_i$ is the ith column of identity matrix.
For $A=(a_{ij})\in \mathbb{R}^{n \times n}$
$$A_i=a_{ii}\qquad \Pi_i'y=y_i e_i$$
where $y_i$ is the ith component of $y$.
\end{block}

\end{frame}

\begin{frame}
\frametitle{PSC and SSC}
Consider residual equation $Ae=r^{\,\mathrm{old}}$, 
and solve it in subspaces
$A_i\hat{e}_i=\Pi_i'r^{\,\mathrm{old}}$
and get $$\hat{e}_i=R_i\,\Pi_i'r^{\,\mathrm{old}}$$
We can update solution in two ways:
\begin{itemize}
\item PSC\,(Parallel):$$u^{\mathrm{new}}=u^{\mathrm{old}}+\sum_{i=1}^J\hat{e_i}$$
\item SSC\,(Successive): $$u^{(1)}=u^{\mathrm{old}}+R_1\,\Pi_1'(f-Au^{\mathrm{old}})$$
$$u^{(2)}=u^{\mathrm{(1)}}+R_2\,\Pi_2'(f-Au^{(1)})$$
$$\cdots \cdots$$
$$u^{\,\mathrm{new}}=u^{\mathrm{(J-1)}}+R_J\,\Pi_J'(f-Au^{(J-1)})$$
\end{itemize}
\end{frame}

\begin{frame}
\begin{block}{Example}
PSC/SSC with subspace decomposition
$$\mathbb{R}^n=\sum_{i=1}^{n}\mathrm{span}\{e_i\}$$
and exact subspace solver $$R_i=A_i^{-1}$$ is Jacobi/Gauss-Seidel iterations.
\end{block}
\end{frame}